Model to study co-evolution of trade an culture

### 2015-03-25 article.tex
working on cultural evolution section

\subsection{Modelisation of Culture}

\xrc{models of cultural change, not culture in general?}

\xrc{what is exactly the definition of culture used in the paper? I would suggest this one: \emph{Culture is socially learned information capable of affecting  individual phenotypes. People acquire culture from other individuals, via teaching or imitation} \cite{richerson_principles_1996}}

The second aspect we wish to model is the evolution of the culture in the Roman empire. The evolutionary framework (generally used in Biology) has been proposed to study the changes of culture and found to be suitable,  particularly in the case of historical and archaeological studies~\cite{lycett_cultural_2015,henrich_evolution_2003}\xrc{henrich's paper is not on archaeology or history, better reference \cite{shennan_evolution_2008}}.

>>>>

\subsection{Neutral models of cultural change}

% 1. the second aspect is cultural change
% 2. an evolutionary framework has explored this
% 3. a large percentage of cultural products exchanged in an economic basis are neutral
% 4. explain neutrality, model of random copy.
% 5. from this perspective the interest of a product for an individual is directly related to its frequency
% 6. this can potentially affect the product as part of a market because offer/demand is related to frequency
% 7. at the same time, frequency will change depending on trade dynamics.

The second component of our model is focused on the dynamics of cultural change. They comprise the collection of processes that promote or inhibit the spread of information by social interaction within a population \cite[3]{boyd_origin_2005}. This evolutionary framework is being used by an increasing number of social scientists, fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}. Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.

Of particular interest to our study are the scenarios where cultural traits are copied by unbiased transmission (i.e. traits which do not have a intrinsic positive or negative value for the individuals adopting them). This situation is often analysed following the genetic theory of neutral evolution \cite{neiman_stylistic_1995}, where the variation of traits is strictly explained by their frequency distribution in the population. There exist a large number of works using this model as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
